### 2017-04-07 paper/evaluation.tex
pass on rq5

%% \begin{enumerate}
%% 	\item How long does it take for test to run in your
%%		environment?
%%	\item Can you briefly define your setup?
%%	\item Do you confirm that your project does not run in
%%		parallel?
%%	\item Select a reason for not using paralellization:
%%		\begin{enumarate}
%%			\item I did not know it was possible;
%%			\item I was concerned with concurrency issues;
%%			\item I use a continuous integration server;
%%			\item Some other reason.
%%		\end{enumerate}
%% \end{enumerate}

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      question~\ref{questionThree}.}
\end{wrapfigure}
%% One of the goals of the first questions is to identify potential
%% discrepancies between our experimental environment and the environment
%% of developers.  Overall, we found that \Fix{...}

Considering question 1, we confirmed that execution time was
compatible with the results we reported in Section~\ref{sec:rqA}.
Furthermore, \emailsCI{} of the participants indicated the use of
Continuous Integration (CI) to run tests, with \emailsDistributed{} of
these participants reporting that test suites were modularized and
those modules were tested independetly in CI servers through different
parameters. A total of \emailsLocal{} participants answered that they
do run tests in their local machines.  Note that CI does not preclude
low-level parallelization.  For example, installations of open-source
CI tools (\eg{}, Jenkins~\cite{jenkins}) in dedicated servers will
still benefit from running tests faster, using test suite
parallelization.

@@

Considering question 2, we found that \emailsSequential{} of the
\emailsProjectsAnswered{} projects indeed did not execute tests in
parallel.  The mismatch is justified by cases where neither of our
checks (static or dynamic) could detect presence of parallelism.  \Fix{elaborate}
\Luis{i looked at those 6 weird projects, and 1 of them contains a
false-negative from rq4, one of them considered the distributed CI
server as parallelism, 2 of them had a custom test runner, and 2 of
them implements parallelism inside the test (they test two+ things in
one test method.}
%% did not confirmed, however,
%% the developers confirmed the need of an extra parameter at the command
%% line to execute in parallel.

From Question III, \emailsA{} of developers do not know that
parallelism is an available configuration for Maven Surefire,
\emailsB{} of developers do not use parallel testing concerned with
concurrency issues, \emailsD{} of developers uses a continuous
integretion server for run tests while working \Luis{here I want to
say that they use it for something like "non-blocking testing" while
developing in a local machine}, \emailsD{} of developers thinks that
it is not worthy the effort, and \emailsNA{} of developers did not
answered the last question, or did not knew an answer.

>>>>

%% \begin{enumerate}
%% 	\item How long does it take for test to run in your
%%		environment?
%%	\item Can you briefly define your setup?
%%	\item Do you confirm that your project does not run in
%%		parallel?
%%	\item Select a reason for not using paralellization:
%%		\begin{enumarate}
%%			\item I did not know it was possible;
%%			\item I was concerned with concurrency issues;
%%			\item I use a continuous integration server;
%%			\item Some other reason.
%%		\end{enumerate}
%% \end{enumerate}
%% One of the goals of the first questions is to identify potential
%% discrepancies between our experimental environment and the environment
%% of developers.  Overall, we found that \Fix{...}

Considering question 1, we confirmed that execution time was
compatible with the results we reported in Section~\ref{sec:rqA}.
Furthermore, \emailsCI{} of the participants indicated the use of
Continuous Integration (CI) to run tests, with \emailsDistributed{} of
these participants reporting that test suites were modularized and
those modules are tested independetly in CI servers through different
parameters. A total of \emailsLocal{} participants answered that they
do run tests in their local machines.  Note, however, that CI does not
preclude low-level parallelization.  For example, installations of
open-source CI tools (\eg{}, Jenkins~\cite{jenkins}) in dedicated
servers will still benefit from running tests faster through low-level
test suite parallelization.

@@

Considering question 2, participants responded that
\emailsSequential{} of the \emailsProjectsAnswered{} projects did not
execute tests in parallel.  This mismatch is justified by cases where
neither of our checks (static or dynamic) could detect presence of
parallelism.  \Fix{elaborate} \Luis{i looked at those 6 weird
  projects, and 1 of them contains a false-negative from rq4, one of
  them considered the distributed CI server as parallelism, 2 of them
  had a custom test runner, and 2 of them implements parallelism
  inside the test (they test two+ things in one test method.}
%% did not confirmed, however,
%% the developers confirmed the need of an extra parameter at the command
%% line to execute in parallel.

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      question~\ref{questionThree}.}
\end{wrapfigure}
Considering question 3, \emailsA{} of developers who answered the
survery did not know that parallelism was available in Maven,
\emailsB{} of developers mentioned that they did not use parallelism
because of concerns with concurrency issues, \emailsD{} of developers
uses a continuous integretion server for run tests while working
\Luis{here I want to say that they use it for something like
  "non-blocking testing" while developing in a local machine},
\emailsD{} of developers thinks that it is not worthy the effort, and
\emailsNA{} of developers did not answered the last question, or did
not knew an answer.
